Automated Formal Synthesis of Optimal Sizing for Stand-alone Solar Photovoltaic Systems

### 2019-08-22 Tex/acmart-master/paper_ICSE_rev0.tex
ICSE paper

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Considering the last two decades, most of the effort related to optimal sizing of stand-alone solar photovoltaic systems was toward optimization criteria and/or objectives. Very few was devoted to the computing method of optimization. There exist various state-of-the-art tools to size solar photovoltaic systems, but they are mainly based on simulations and do not cover all aspects of the design-space. We present a sound and automated approach to synthesize optimal sizing of stand-alone PV systems using program synthesis. The focus is in a new computer optimization method. In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first, starting from user requirements and a list of commercial equipment, we synthesize a feasible sizing solution of a given stand-alone PV system; secondly, the optimal solution is then verified via symbolic model checking to guarantee that the cost is the lowest among the feasible solutions; if the verification step fails, a bound is adjusted and the process iterates until an optimal sizing is obtained. Therefore, candidate solutions are derived from financial analysis of the obtained sizing. Our synthesis method is novel and unprecedented to streamline the design of PV systems. Experimental results show that our synthesis method is able to synthesize within an acceptable run-time the optimal PV system sizing of two different intricate case studies.
\end{abstract}

@@

However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored, its can offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}. Here, we use counterexample guided inductive synthesis (CEGIS) variation for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data. Given a correctness specification $\sigma$, our method uses that as starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$. In particular, in each iteration, we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost. The optimal solution is then verified via symbolic model checking; if the verification step succed, the method returns to the synthesis phase and a counterexample is provided to the synthesis engine and the process iterates until an optimal sizing is obtained from financial analysis.

@@

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.85\columnwidth]{fig2_rev.jpg}
	\caption{CEGIS applied to PV system sizing.}
	\label{Counter-Example-Guided-Inductive-Synthesis}
\end{figure}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
Considering the last two decades, most of the effort related to optimal sizing of stand-alone solar photovoltaic systems was toward optimization criteria and/or objectives. Very few was devoted to the computing method of optimization. There exist various state-of-the-art tools to size solar photovoltaic systems, but they are mainly based on simulations and do not cover all aspects of the design-space. We present a sound and automated approach to synthesize optimal sizing of stand-alone PV systems using program synthesis. The focus is in a new computer optimization method. In particular, our variant of counterexample guided inductive synthesis (CEGIS) approach has two phases: first, starting from design requirements and a list of commercial equipment, we synthesize a feasible sizing solution of a given stand-alone PV system; secondly, the optimal solution is then verified via symbolic model checking to guarantee that the cost is the lowest among the feasible solutions; if the verification step does not fails, a bound is adjusted and the process iterates until an optimal sizing is obtained. Therefore, candidate solutions are derived from financial analysis of the obtained sizing. Our synthesis method is novel and unprecedented to streamline the design of PV systems. Experimental results show that our synthesis method is able to synthesize within an acceptable run-time the optimal PV system sizing of two different case studies very common in rural areas.
\end{abstract}

@@

However, formal methods based on \textit{symbolic model checking} and its application to synthesize PV systems have not been further explored, its can offer a great potential to obtain a more effective design process to PV systems~\cite{ClarkeHV18}. Here, we use counterexample guided inductive synthesis (CEGIS) variation for synthesizing optimal sizing of stand-alone PV systems using commercial equipment data. Given a correctness specification $\sigma$, our method uses that as starting point and then iteratively produces a sequence of candidate solutions that satisfy $\sigma$. In particular, in each iteration, we synthesize sizing of stand-alone PV systems but that may not achieve the lowest cost. The optimal solution is then verified via symbolic model checking; if the verification step fails, a counterexample is generated with the optimal cost for the feasible solution found at the synthesis phase. If the verification succeeds, the  method returns to the synthesis engine, with a new bound of search (new possible optimal cost) and the process iterates until an optimal sizing is obtained from financial analysis.

The proposed method differs from traditional CEGIS because the counterexample is not used from the formal verification to create a set of input values for the synthesis phase. Moreover, the set of feasible PV sizing solutions from the synthesis phase can be tested more than once at the verification phase, depending on the bound used in each iteration.

@@

Program synthesis addresses an age-old issue in computer science: can a computer program itself? The aim is to avoid errors inputted by programmers during coding (bugs) and to improve productivity. Moreover, to compound this risk, today’s highly asynchronous, heterogeneous, and distributed systems are even more prone to programming errors. And if we could just tell the computer what it should do — provide it with a specification of what we want — and let it do the legwork of figuring out how to do it? This is the promise of program synthesis: given a specification, automatically generate a program that satisfies it~\cite{ACMSigplan}.

Before the computer can automatically generate a program, we need to give it a specification of what the program should do. The specification needs to describe the program’s desired behavior in enough detail to ensure the program does what we want, but ideally, it should be much simpler than the program itself, since otherwise we may as well just write the program~\cite{ACMSigplan}. In recent years, synthesis has been used for digital control systems design as well, however without application to solar PV systems~\cite{Abateetal2017, Abate2017}.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=0.85\columnwidth]{fig2_rev2.jpg}
	\caption{CEGIS applied to PV system sizing.}
	\label{Counter-Example-Guided-Inductive-Synthesis}
\end{figure}
